Clouds and Radiation in a mock-Walker Circulation

### 2020-05-01 Silvers_WalkerCell.tex
mostly text changes to Silvers_WalkerCell.tex and addition of references to the bib file for WalkerCell

It is also clear that the tropical Pacific plays an important role in the response of the climate to radiative perturbations. 
Recent work has shown that the interactions between clouds, patterns of Sea Surface Temperature (SST), and the circulation 
in the tropical Pacific play an important role in determining the cloud feedback and the decadal 
variability of the climate feedback 
\cite<e.g.,>[]{Andrews_Webb_2018, Zhou_etal_2016, Silvers_etal_2018, Fueglistaler_2019}.
While the Hadley circulation connects the tropics with the midlatitudes,  
the Walker circulation is one of the primary mechanisms by which the clouds, SST and circulations 
are coupled to each other in the tropics.  
%While the meridional temperature gradient is a fundamental driver of the large-scale circulation, and 
%the Coriolis force is critical in determining the characteristics of tropical waves and the tropical 
%extra-tropical connections, 
We propose that focusing on the Walker Circulation can lead to new insights into 
several questions that are critical to a better understanding of the tropical climate and cloud processes.    
These questions include: 
\begin{itemize}
  \item{How do clouds influence the overturning circulation?}
  \item{To what extent are the deep convective clouds and the low-level clouds coupled through 
  the overturning circulation?}
  \item{When simulating tropical overturning circulations, how well does a GCM compare to a CRM?}  
\end{itemize}
%These interactions are influenced not only by the Walker circulation, but also the Hadley 
%cell and convectively coupled tropical waves.  
In global and Earth-like GCM simulations, the interplay between the overturning 
circulation and clouds is difficult to disentangle from other active processes such as
the Hadley cell and convectively coupled tropical waves.  
%the large-scale circulation and clouds do not 
%act on each other in isolation but are also influenced by a host of other phenomena such as 
%the Hadley cell and convectively coupled tropical waves.  
Most of the studies with CRMs that have focused on the tropical overturning circulation in a more idealized 
context have been restricted to relatively small domain sizes and highly simplified physics parameterizations.  
The result is a gap in the types of simulation for this region that is so important to our 
understanding of clouds in the Earth's climate system.  
%The Walker circulation embodies an ideal combination of physical processes that can help us to connect the findings from CRMs, 
%GCMs, and the observed world.

% Deep convective towers release vast amounts of latent heat into the atmosphere and are part of the system
% that transports so much energy poleward.  Trade-wind cumulus and stratocumulus clouds influence the 
% Pacific-decadal oscillation and ENSO as well as reflecting vast amounts of insolation back to space.
% This region of the globe has been recognized to be of critical importance to the global energy budget 
% for decades (Rhiel and Malkus ?, Pierrehumbert, 1995?)

@@

All simulations use a nonhydrostatic dynamical core, with prescribed SSTs and a doubly periodic domain which is elongated in the zonal 
direction allowing for three dimensional simulations but with a reduced computational cost relative to the default global domain.  
The domain is flat, not rotating, and has uniform and constant insolation.
The lower boundary of the domain is a water covered surface with the SST prescribed as a time invariant Gaussian function 
which is 4K warmer in the center (301K/27.85C) of the domain then 
at the edges (297K/23.85C).  
To develop the model configuration used for these experiments we started with the same code base as that of the 
recently developed atmospheric global climate model AM4.0 \cite{Zhao_etal18a, Zhao_etal18b} (Z18a and Z18b hereafter).
AM4.0 uses the GFDL finite-volume cubed-sphere dynamical core FV3 (Harris and Lin, 2013) 
which can solve either the hydrostatic primitive equations or the nonhydrostatic fully compressible Euler equations
over a wide range of resolutions.   
Current generation global GFDL models use 
a cubed-sphere grid that is composed of six tiles.  We use the model on a single doubly-periodic
tile.  This allows the grid-spacing and domain size to be easily changed to minimize the cost of computations.
This study focuses on experiments with grid-spacing of 100km, 25km, 2km, and 1km on several different
sizes of domain.  Additional details are given in Table \ref{tab:experimentspecs}.

The default AM4.0 physics we use includes interactive radiation, parameterized deep- and shallow-convection, 
a large-scale cloud scheme, and a boundary layer 
scheme as described in Z18a,b, and the references therein.  The prognostic moisture variables are the specific 
humidity (q), liquid (ql) and frozen water (qi), and cloud fraction.  The top of the model domain is at 1 hPa, with 33 vertical 
levels and a sponge layer extending downward to 8 hPa.  The kilometer of atmosphere just above the surface is resolved by 
8 model levels.  The changes made to the default AM4.0 physics configuration are as follows.  The cloud-aerosol 
interactions were turned off to focus on the interaction between clouds, radiation, and the circulation.  The gravity wave drag 
parameterization was turned off 
%(do_cg_drag set to .f.; Alexander-Dunkerton gravity wave drag) 
in order to reduce large oscillations which developed in the horizontal wind field near the top of the model domain.  
The convection, radiation, large-scale cloud, microphysics, and turbulence parameterizations all remain the same 
as in AM4.0.   Thus for the experiments with convective parameterization (grid-spacing of 25km and 100km), the 
physics are very similar to those of AM4.0.  
This configuration of AM4.0 physics was initially used by \citeA{Popp_Silvers_2017} and as the aquaplanet model that 
was used as part of GFDL's contribution to the CFMIP component of CMIP6.

@@

One tool that has been commonly used to infer the influence of clouds on a model simulation is to make the clouds invisible to the radiation.  
This can tell us the extent to which the specific location of the clouds matters to the radiative interaction with the 
atmospheric state.   This method was originally pioneered by \citeA{Slingo_Slingo_1988} and \citeA{Randall_etal_1989}.  
More recently, it has been
implemented as part of the CFMIP series of experiments \cite{Stevens_etal_2012, Webb_etal_2017}.
In the AM4 code, this is done separately for the longwave (LW) and shortwave radiation.  
In this study we compare control experiments, in which clouds and radiation are fully interactive with experiments in which clouds are invisible to the LW radiation.  
These experiments in which clouds do not interact with the LW radiation are referred to as Longwave Cloud Radiative Effect Off (LWCRE-off).  
For the LWCRE-off experiments, both the LW and shortwave radiation are present and interact with 
the atmospheric state, the clouds still interact with the shortwave radiation, and they still precipitate.   
Turning off the LWCRE would have a large impact on the surface budget of a coupled model.  
However, because there is no land in our simulations and the SST is held fixed, the energetics of our experiments are not as
strongly effected as might be expected.  For this reason, experiments with only a water surface at the lower boundary and 
fixed SST are the ideal configuration to utilize the LWCRE-off experiments as a way of diagnosing how clouds interact with 
the atmospheric state.

The experiments with 100km and 25km grid-spacing have been run for 5 years while the 
1km and 2km experiments were run for 6 months.  Experiments with parameterized convection are labelled with a P prefix, followed
by a number indicating the grid-spacing in kilometers while the experiments with explicit convection (no parameterized convection) will be 
labelled with an E prefix, followed by the appropriate number.  Thus P25 refers to an experiment with parameterized convection using a 
grid-spacing of 25km, while E25 refers to an experiment that is identical to P25 except that the convective parameterization is turned off. 
The naming convection for each of the experiments shown in Table \ref{tab:experimentspecs}.   
Throughout this paper the P100 and P25 experiments, both with and without the LWCRE on are referred to as `GCM-like' and
`CRM-like'.  The GCM-like experiments only differ from traditional GCMs in the non-global domain and lack of rotation.  
Using the CRM-like terminology acknowledges that this model configuration has not been developed as a CRM, has a vertical resolution that is more coarse than other CRMs, and uses the large-scale cloud scheme from the AM4.0/CM4.0 GCM.

@@

The E1 and E2 simulations are in many ways similar to the configuration of so-called cloud resolving models.  
In particular both the deep and shallow convective parameterizations are turned off, and the threshold of grid-cell mean relative humidity 
which triggers new clouds is changed from the default value of 0.8 to 1.0.  While a grid spacing of 1 or 2km is clearly not small enough
to resolve all clouds, it is small enough to resolve cloud-systems and medium to larger sized clouds.  The primary 
difference between the CRM simulations presented in this paper and those of more established CRMs such as  the 
System for Atmospheric Modeling (SAM; see Khairoutdinov and Randall, 2003) is that our model
has a much coarser vertical resolution and a prognostic large-scale cloud scheme inherited from the GCM.  The large-scale cloud
scheme is based on the \citeA{Tiedtke1993} parameterization.  This was originally designed to be used with GCMs having a coarse grid-spacing
and includes prognostic equations for both cloud liquid water and cloud fraction.  
However, we are not aware of a fundamental problem in using the Tiedtke scheme for large-scale clouds in a model with 1km grid-spacing.   
The advantage is retaining the identical cloud scheme as is used in the parent GCM; the disadvantage is the greatly increased complexity of the 
cloud computations relative to many other cloud resolving models.

\begin{table}
\begin{center}
\caption{Domain mean precipitation ($\overline{\rm{P}}$), outgoing longwave radiation 
($\overline{\rm{OLR}}$), precipitable water ($\overline{\rm{PW}}$), and subsidence fraction (SF)  
or fraction of domain that is subsiding at the 532 hPa level.
Values in parenthesis correspond to LWCRE-off experiments.}
    \begin{tabular}{*{5}{c}}
    \hline
    \hline
    \\
 Name &   $\overline{\rm{P}} (\mathrm{mm \,d^{-1}})$ & $\overline{\rm{OLR}} (\rm{W \, m^{-2}})$ & $\overline{\rm{PW}} (\rm{mm})$ & SF   \\ \hline
  P100L   &  4.1 (3.5)   &  283.1 (286.9)  & 36.6 (31.3)  & 0.89 (0.61)      \\ 
    \\
  P100 &   3.9 (3.7)   &  283.2 (296.4)  & 28.0 (26.8) & 0.73 (0.71)           \\  
    \\
  P25L &   4.0 (3.8)  &  281.2 (290.7)   & 35.0 (32.9) & 0.78 (0.69)          \\  
    \\
  P25  &   3.8 (3.7)    & 282.9 (293.6)   & 27.4 (26.4) & 0.80 (0.72)          \\  
    \\
 E25  & 3.7 (3.5)    &   271.9 (286.8)   & 28.7 (27.3) & -            \\  
    \\
 E2   &  3.1 (3.4)   &  266.2 (285.5)    & 27.0 (25.2) & 0.83 (0.77)           \\ 
    \\
 E1   &  3.3 (3.7)   &  269.3 (289.2)    & 27.3 (26.5) & 0.78 (0.78)         \\  \hline

@@

\section{The Influence of Interactive Radiation on Clouds and the Organization of the mock-Walker Circulation}

@@

The mock-Walker Circulation that emerges from these simulations is shown in Figures \ref{fig:rh_psi_P25vsE25} and 
\ref{fig:precip_vertvel} to be characterized by a strong overturning circulation with precipitation focused over the warmer 
SSTs and a humid boundary layer across the full length of the domain.    Superposing the circulation and relative 
humidity (Figure \ref{fig:rh_psi_P25vsE25}) clearly shows the results of subsidence driven 
drying over regions with cooler SST (at the edges of the domain) and the strong moistening that results from ascent over the region of high
SST (in the center of the domain) where the latent heat flux is large.   The circulation is illustrated by the combination of 
the mass streamfunction in Figure \ref{fig:rh_psi_P25vsE25} and the vertical velocity in Figure \ref{fig:precip_vertvel}.   
The mass streamfunction illustrates the 
two-dimensional flux of mass and includes information from both the horizontal and vertical velocity components.
High concentrations of condensate are present in the mid-troposphere over the warmer SSTs, while the regions with subsiding 
circulations are dry ($< 20\% RH$) above about $900\, \rm{hPa}$.  
Two distinct circulation cells are present with one below, and one above $500 \, \rm{hPa}$.   
%Deep-convective activity dominates the region over the warm pool, shallow convection is common 
%over a wider range of SSTs, and for the most part stratocumulus clouds are absent.
It is worth noting that this state of deep overturning circulation with convection 
and precipitation concentrated in the region of ascent and a dry troposphere in the regions of descent is common
to the Walker circulation, tropical two-box models (e.g. Pierrehumbert, 1995, Larson et al., 1999), and 
experiments of radiative convective equilibrium which equilibrate to a state with deep-overturning circulations 
and convective aggregation (e.g. Bretherton et al., 2005).

@@

Previous studies have shown that Cloud Radiative Effects (CREs) act to strengthen and contract an 
overturning circulation 
\cite<e.g.>[]{Fermepin_Bony_2014, Harrop_Hartmann_2016b, Popp_Silvers_2017,Albern_etal_2018}; Li et al??).  This is 
due to an increased low-level flux
of moist static energy into the convective regions.  While our mock-Walker circulation is distinct from radiative
convective equilibrium and the resulting convective self-aggregation, there are obvious similarities between our 
region of persistent deep convection and a state of aggregation (work in a citation of M{\"u}ller and Hohenegger, 2019).   
\textit{RCE studies showing convective self-aggregation have illustrated the 
dependence of the details of the aggregation on the domain size, the physics, or other details of the 
study.  Using a mock-Walker circulation allows one to study controlled convective aggregation rather 
then spontaneous convective self-aggregation.  The added constraint of the fixed warm-patch could lead 
to clarification of the processes that drive important atmospheric interactions.}
One of the simplest measures of convective aggregation and the large-scale circulation is the fraction of the domain 
in which the air is subsiding, referred to as the subsidence fraction (SF).  
As convection becomes more organized, or aggregated, the SF will increase.  We expect 
for an overturning circulation that a contraction of the convective region would result in a larger subsidence 
fraction.  This is precisely what we see in Table \ref{tab:experimentmeans}.  For each of our experiments, the cases with LWCRE-on
have a larger SF (with the exception of E1, for which SF is constant).  Much has been written about a 
dependence of aggregated atmospheric states on temperature (\citeA{Khairoutdinov2010}; \citeA{Wing2014}; Cronin and Wing, 2017).  
While there does appear to be a dependence 
on temperature, Table \ref{tab:experimentmeans} illustrates how much the aggregated 
state can vary among experiments with identical SST.  Having a prescribed SST warm 
patch ensures that the simulations will be `aggregated' to some degree.  
The SF indicates not only whether an 
experiment is aggregated, but also the spatial extent of the overturning circulation.  
Given identical SSTs, the  range of different SFs provide a measure of variability that is driven entirely by the interactions between 
convection, radiation, and the large-scale circulation.

@@

The evolution in time of the precipitation field clearly illustrates how much the spatial distribution can vary as a 
function of domain size, parameterization of convection, and the effect of the LW radiation due to clouds. 
Shown in Figures {\ref{fig:domdep}} and {\ref{fig:domdep_lwoff}} are Hovm{\"o}ller plots of precipitation after 
averaging along the short horizontal dimension.  The four panels show simulations with a grid-
spacing of $25\, \rm{km}$ on a domain with a horizontal length of $4000\, \rm{km}$ and $16000\, \rm{km}$, and 
simulations with a grid-spacing of $100\, \rm{km}$ on a grid with a horizontal length of $4000\, \rm{km}$ and 
$16000\, \rm{km}$.  Figure  {\ref{fig:domdep_lwoff}} shows the equivalent simulations with LWCRE-off.

At all resolutions the Hovm{\"o}ller plots show that the LWCRE acts to concentrate the 
precipitation over a smaller geographic extent.   This is consistent with previous work showing that CREs 
strengthen an overturning circulation and narrow the region of deep convection (see \citeA{Harrop_Hartmann_2016b}; 
\citeA{Popp_Silvers_2017}; \citeA{Albern_etal_2018}; \citeA{Dixit_etal_2018}  etc.).  The structure of the precipitation changes more 
as a function of domain size than it does as a function of resolution. 
On the large domains, the difference between experiments with and without LWCRE is extreme.  
In contrast to the control experiments in Figure {\ref{fig:domdep}} which all show a narrow region of strong 
precipitation meandering within about 500 km of the SST maximum at the center of the domain,  the large domain experiments 
without the LWCRE have an 8000 km wide region in which the precipitation consistently develops (Figure {\ref{fig:domdep_lwoff}).  
Smaller cells and lines of precipitation develop within this large area with no apparent preference to settle
over the center of the domain where the SST is a maximum.  As previously noted, 
these GCM-like simulations equilibrate after approximately 50 days.  There is also a dramatic change in 
the distribution of precipitation on the $4000\, \rm{km}$ domain simulations after almost 2 years.   The domain mean 
precipitation does not significantly change in these cases, only the spatial structure.

@@

% new Hovmoller diagram
\begin{figure}
 % \includegraphics[angle=90, width=0.95\columnwidth]{walkerfigs/hov_precip_4pan_vert_lwcreon.eps}
  \includegraphics[width=0.95\columnwidth]{walkerfigs/hov_precip_lwon_huge.eps}
  \caption{Evolution of precipitation through 3 years of simulation for experiments with a grid spacing of
  25km and 100km.  Panel A shows the 100km experiment on the large domain 100km, (P100L); 
  B, 25km on large domain, (P25L); C, 100km on small domain, (P100); and D, 25km on small domain 
  (P25).  For each resolution, the only difference between the two experiments shown is a domain length of 
  16,000 km or 4,000 km.  All cases have an SST of 301 K at the center and 297K at the edges.  The plotted values are: 1,5,10,15,20,30,40,50,60,70,80,90.  Data have been averaged over the short horizontal dimension.}
  \label{fig:domdep}
\end{figure}

@@

We now show results from our simulations of a mock-Walker circulation with both a GCM-like and a CRM-like configuration.  
In this section we focus on simulations with grid-spacing of 
1km, 2km, and 25km all on a domain with the width of 4,000 km for the long side.  
The models agree on 
the basic circulation pattern and the spatial distribution of mid-tropospheric condensate.  
However, the E25/P25 simulations produce 4 to 5 times as much low-level cloud and 
condensate as E2/E1 in the subsiding regions.   As a result the models have a different response 
to the LWCRE.  The differences in the boundary layer of the wind, enthalpy flux, and 
temperature among the models result in different spatial distributions and amounts of 
precipitation in the equilibrated state.

>>>>

It is also clear that the tropical Pacific plays an important role in the response of the climate to radiative perturbations. 
Recent work has shown that the interactions between clouds, patterns of Sea Surface Temperature (SST), and the circulation 
in the tropical Pacific play an important role in determining the cloud feedback and the decadal 
variability of the climate feedback 
\cite<e.g.,>[]{Andrews_Webb_2018, Zhou_etal_2016, Silvers_etal_2018, Fueglistaler_2019}.
While the Hadley circulation connects the tropics with the midlatitudes,  
the Walker circulation is one of the primary mechanisms by which the clouds, SST and circulations 
are coupled to each other in the tropics.  
%While the meridional temperature gradient is a fundamental driver of the large-scale circulation, and 
%the Coriolis force is critical in determining the characteristics of tropical waves and the tropical 
%extra-tropical connections, 
We propose that focusing on the Walker Circulation can lead to new insights into 
several questions that are critical to a better understanding of the tropical climate and cloud processes.    
These questions include: 
\begin{itemize}
  \item{How do clouds influence the overturning circulation?}
  \item{To what extent are the deep convective clouds and the low-level clouds coupled through 
  the overturning circulation?}
  \item{When simulating tropical overturning circulations, how well does a GCM compare to a CRM?}  
\end{itemize}
%These interactions are influenced not only by the Walker circulation, but also the Hadley 
%cell and convectively coupled tropical waves.  
In global and Earth-like GCM simulations, the interplay between the overturning circulation and clouds is difficult to disentangle from other 
active processes such as the Hadley cell and convectively coupled tropical waves.  
Most of the studies with CRMs that have focused on the tropical overturning circulation in a more idealized context have been restricted to 
relatively small domain sizes and highly simplified physics parameterizations.  
The result is a gap in the types of simulation for this region that is so important to our understanding of clouds in the Earth's climate system.

% Deep convective towers release vast amounts of latent heat into the atmosphere and are part of the system
% that transports much energy poleward.  Trade-wind cumulus and stratocumulus clouds influence the 
% Pacific-decadal oscillation and ENSO as well as reflecting vast amounts of insolation back to space.
% This region of the globe has been recognized to be of critical importance to the global energy budget 
% for decades (Rhiel and Malkus ?, Pierrehumbert, 1995?)

@@

All simulations use a nonhydrostatic dynamical core, with prescribed SSTs and a doubly periodic domain which is elongated in the zonal 
direction allowing for three dimensional simulations but with a reduced computational cost relative to the default global domain.  
The domain is flat, non rotating, and has uniform and constant insolation.
The lower boundary is a water covered surface with the SST prescribed as a time invariant Gaussian function 
which is 4K warmer in the center (301K/27.85C) of the domain then 
at the edges (297K/23.85C).  
To develop the model configuration used for these experiments we started with the same code base as that of the 
recently developed atmospheric global climate model AM4.0 \cite{Zhao_etal18a, Zhao_etal18b} (Z18a and Z18b hereafter).
AM4.0 uses the GFDL finite-volume cubed-sphere dynamical core FV3 (Harris and Lin, 2013) 
which can solve either the hydrostatic primitive equations or the nonhydrostatic fully compressible Euler equations
over a wide range of resolutions.   
Current generation global GFDL models use a cubed-sphere grid composed of six tiles.  We use the model on a single doubly-periodic
tile.  This allows the grid-spacing and domain size to be easily changed to minimize the cost of computations.
This study focuses on experiments with grid-spacing of 100km, 25km, 2km, and 1km on several different
sizes of domain.  Additional details are given in Table \ref{tab:experimentspecs}.

The default AM4.0 physics we use includes interactive radiation, parameterized deep- and shallow-convection, 
a large-scale cloud scheme, and a boundary layer 
scheme as described in Z18a,b, and the references therein.  The prognostic moisture variables are the specific 
humidity (q), liquid (ql) and frozen water (qi), and cloud fraction.  The top of the model domain is at 1 hPa, with 33 vertical 
levels and a sponge layer extending downward to 8 hPa.  The kilometer of atmosphere just above the surface is resolved by 
8 model levels.  Changes made to the default AM4.0 physics in this study are as follows.  The cloud-aerosol 
interactions were turned off to focus on the interaction between clouds, radiation, and the circulation.  The gravity wave drag 
parameterization was turned off 
%(do_cg_drag set to .f.; Alexander-Dunkerton gravity wave drag) 
in order to reduce large oscillations which developed in the horizontal wind field near the top of the model domain.  
The convection, radiation, large-scale cloud, microphysics, and turbulence parameterizations all remain the same 
as in AM4.0.   Thus for the experiments with convective parameterization (grid-spacing of 25km and 100km), the 
physics are very similar to those of AM4.0.  
This configuration of AM4.0 physics was initially used by \citeA{Popp_Silvers_2017} and more recently for the aquaplanet model
used as part of GFDL's contribution to the CFMIP component of CMIP6.

@@

One technique that has been commonly used to infer the influence of clouds on the atmospheric is to make the clouds invisible to the radiation.  
Breaking the two-way interaction between clouds and radiation can then be used as a diagnostic tool.  
%This can tell us the extent to which the specific location of the clouds matters to the radiative interaction with the atmospheric state.   
This method was originally pioneered by \citeA{Slingo_Slingo_1988} and \citeA{Randall_etal_1989}.  
More recently, it has been
implemented as part of the CFMIP series of experiments \cite{Stevens_etal_2012, Webb_etal_2017}.
In the AM4 code, this is done separately for the longwave (LW) and shortwave radiation.  
In this study we compare control experiments, in which clouds and radiation are fully interactive with experiments in which clouds are invisible to the LW radiation.  
These experiments in which clouds do not interact with the LW radiation are referred to as Longwave Cloud Radiative Effect Off (LWCRE-off).  
For the LWCRE-off experiments, both the LW and shortwave radiation are present and interact with 
the atmospheric state, the clouds still interact with the shortwave radiation, and they still precipitate.   
Turning off the LWCRE would have a large impact on the surface budget of a coupled model.  
However, because there is no land in our simulations and the SST is held fixed, the energetics of our experiments are not as
strongly effected as might be expected.  For this reason, experiments with only a water surface at the lower boundary and 
fixed SST are an ideal configuration to utilize the LWCRE-off experiments as a way of diagnosing how clouds interact with 
the atmospheric state.

The experiments with 100km and 25km grid-spacing have been run for 5 years while the 
1km and 2km experiments were run for 6 months.  Experiments with parameterized convection are labelled with a P prefix, followed
by a number indicating the grid-spacing in kilometers while the experiments with explicit convection (no parameterized convection) will be 
labelled with an E prefix, followed by the appropriate number.  Thus P25 refers to an experiment with parameterized convection using a 
grid-spacing of 25km. %, while E25 refers to an experiment that is identical to P25 except that both the deep and shallow convective parameterizations have been turned off. 
The naming convection for each of the experiments shown in Table \ref{tab:experimentspecs}.   
Throughout this paper the P100 and P25 experiments, with and without the LWCRE are referred to as `GCM-like' and
`CRM-like'.  The GCM-like experiments only differ from traditional GCMs in the non-global domain and lack of rotation.  
The CRM-like terminology acknowledges that this configuration % has not been developed as a CRM, 
has a vertical resolution that is coarser than many CRMs, and uses the large-scale cloud scheme from the AM4.0/CM4.0 GCM.

@@

The E1 and E2 simulations are in many ways similar to the configuration of so-called cloud resolving models.  
In particular all convection is explicitly resolved, %both the deep and shallow convective parameterizations are turned off, 
and the threshold of grid-cell mean relative humidity which triggers new clouds is changed from the default value of 0.8 to 1.0.  
While a grid spacing of 1 or 2km is clearly not small enough
to resolve all clouds, it is small enough to resolve cloud-systems and medium to larger sized clouds.  
%The primary difference between the CRM simulations presented in this paper and those of more established CRMs such as  the 
%System for Atmospheric Modeling (SAM; see Khairoutdinov and Randall, 2003) is that our model
%has a much coarser vertical resolution and a prognostic large-scale cloud scheme inherited from the GCM.  
The large-scale cloud scheme is based on the \citeA{Tiedtke1993} parameterization.  
This was originally designed to be used with GCMs having a coarse grid-spacing and includes prognostic equations for both 
cloud liquid water and cloud fraction.  
However, we are not aware of a fundamental problem in using the Tiedtke scheme for large-scale clouds in a model with 1km grid-spacing.   
The advantage is retaining the identical cloud scheme as is used in the parent GCM; the disadvantage is the greatly increased complexity of the 
cloud computations relative to many other cloud resolving models.

\begin{table}
\begin{center}
\caption{Domain mean precipitation ($\overline{\rm{P}}$), outgoing longwave radiation 
($\overline{\rm{OLR}}$), precipitable water ($\overline{\rm{PW}}$), and subsidence fraction (SF)  
or fraction of domain that is subsiding at the 532 hPa level.
Values in parenthesis correspond to LWCRE-off experiments.}
    \begin{tabular}{*{5}{c}}
    \hline
    \hline
    \\
 Name &   $\overline{\rm{P}} (\mathrm{mm \,d^{-1}})$ & $\overline{\rm{OLR}} (\rm{W \, m^{-2}})$ & $\overline{\rm{PW}} (\rm{mm})$ & SF   \\ \hline
  P100L   &  4.1 (3.5)   &  283.1 (286.9)  & 36.6 (31.3)  & 0.89 (0.61)      \\ 
    \\
  P100 &   3.9 (3.7)   &  283.2 (296.4)  & 28.0 (26.8) & 0.74 (0.73)           \\  
    \\
  P25L &   4.0 (3.8)  &  281.2 (290.7)   & 35.0 (32.9) & 0.78 (0.70)          \\  
    \\
  P25  &   3.8 (3.7)    & 282.9 (293.6)   & 27.4 (26.4) & 0.80 (0.74)          \\  
    \\
 E25  & 3.7 (3.5)    &   271.9 (286.8)   & 28.7 (27.3) & 0.72 (0.75)            \\  
    \\
 E2   &  3.1 (3.4)   &  266.2 (285.5)    & 27.0 (25.2) & 0.82 (0.75)           \\ 
    \\
 E1   &  3.3 (3.7)   &  269.3 (289.2)    & 27.3 (26.5) & 0.80 (0.80)         \\  \hline

@@

\section{Cloud Radiative Interactions and the Organization of a mock-Walker Circulation}

@@

The mock-Walker Circulation that emerges from these simulations is shown in Figures \ref{fig:rh_psi_P25vsE25} and 
\ref{fig:precip_vertvel} to be characterized by a strong overturning circulation with precipitation focused over the warmer 
SSTs and a humid boundary layer across the full length of the domain.    Superposing the circulation and relative 
humidity (Figure \ref{fig:rh_psi_P25vsE25}) clearly shows the results of subsidence driven 
drying over regions with cooler SST (at the edges of the domain) and the strong moistening that results from ascent over the region of high
SST (in the center of the domain) where the latent heat flux is large.   The circulation is illustrated by the combination of 
the mass streamfunction in Figure \ref{fig:rh_psi_P25vsE25} and the vertical velocity in Figure \ref{fig:precip_vertvel}.   
The mass streamfunction illustrates the 
two-dimensional flux of mass and includes information from both the horizontal and vertical velocity components.
The lower panels of Figure \ref{fig:rh_psi_P25vsE25} show high concentrations of condensate are present in the mid-troposphere over the warmer SSTs, while the regions with subsiding 
circulations are dry ($< 20\% RH$) above about $900\, \rm{hPa}$.  
Two distinct circulation cells are present with one below, and one above $500 \, \rm{hPa}$.   
%Deep-convective activity dominates the region over the warm pool, shallow convection is common 
%over a wider range of SSTs, and for the most part stratocumulus clouds are absent.
This state of deep overturning circulation with convection 
and precipitation concentrated in the region of ascent and a dry troposphere in the regions of descent is common
to the Walker circulation, tropical two-box models (e.g. Pierrehumbert, 1995, Larson et al., 1999), and 
experiments of radiative convective equilibrium which equilibrate to a state with deep-overturning circulations 
and convective aggregation (e.g. Bretherton et al., 2005).

@@

Previous studies have shown that Cloud Radiative Effects (CREs) act to strengthen and contract an 
overturning circulation 
\cite<e.g.>[]{Fermepin_Bony_2014, Harrop_Hartmann_2016b, Popp_Silvers_2017,Albern_etal_2018}. 
%Li et al?? 
This is due to an increased low-level flux
of moist static energy into the convective regions.  While our mock-Walker circulation is distinct from radiative
convective equilibrium and the resulting convective self-aggregation, there are obvious similarities between our 
region of persistent deep convection and a state of aggregation (work in a citation of M{\"u}ller and Hohenegger, 2019).   
%\textit{RCE studies showing convective self-aggregation have illustrated the dependence of the details of the 
%aggregation on the domain size, the physics, or other details of the study. } 
Using a mock-Walker circulation allows one to study controlled convective aggregation rather then spontaneous convective self-aggregation.  
The added constraint of the fixed warm-patch could lead to clarification of the processes that drive important atmospheric interactions.
One of the simplest measures of convective aggregation and the large-scale circulation is the fraction of the domain 
in which the air is subsiding, referred to as the subsidence fraction (SF).  
As convection becomes more organized, or aggregated, the SF will increase.  We expect 
for an overturning circulation that a contraction of the convective region would result in a larger subsidence 
fraction.  This is precisely what we see in Table \ref{tab:experimentmeans}.  For each of our experiments, the cases with LWCRE-on
have a larger SF (with the exception of E1, for which SF is constant).  Much has been written about a 
dependence of aggregated atmospheric states on temperature \cite{Khairoutdinov2010, Wing2014, Cronin2017}.  
While there does appear to be a dependence 
on temperature, Table \ref{tab:experimentmeans} illustrates how much the aggregated 
state can vary among experiments with identical SST.  Having a prescribed SST warm 
patch ensures that the simulations will be `aggregated' to some degree.  
The SF indicates not only whether an 
experiment is aggregated, but also the spatial extent of the overturning circulation.  
Given identical SSTs, the  range of different SFs provide a measure of variability that is driven entirely by the interactions between 
convection, radiation, and the large-scale circulation.

@@

The evolution in time of the precipitation field clearly illustrates how much the spatial distribution can vary as a 
function of domain size, parameterization of convection, and the effect of the LW radiation due to clouds. 
Shown in Figures {\ref{fig:domdep}} and {\ref{fig:domdep_lwoff}} are Hovm{\"o}ller plots of precipitation after 
averaging along the short horizontal dimension.  The four panels show simulations with two grid-spacings 
($25\, \rm{km}$ and $100\, \rm{km}$) using two different domain sizes (long horizontal length of $4000\, \rm{km}$ and $16000\, \rm{km}$).
%, and simulations with a grid-spacing of $100\, \rm{km}$ on a grid with a horizontal length of $4000\, \rm{km}$ and $16000\, \rm{km}$.  
Figure  {\ref{fig:domdep_lwoff}} shows the equivalent simulations with LWCRE-off.

At all resolutions the Hovm{\"o}ller plots show that the LWCRE acts to concentrate the 
precipitation over a smaller geographic extent.   This is consistent with previous work showing that CREs 
strengthen an overturning circulation and narrow the region of deep convection (see \citeA{Harrop_Hartmann_2016b}; 
\citeA{Popp_Silvers_2017}; \citeA{Albern_etal_2018}; \citeA{Dixit_etal_2018}  etc.).  The structure of the precipitation changes more 
as a function of domain size than it does as a function of resolution. 
On the large domains, the difference between experiments with and without LWCRE is extreme.  
In contrast to the control experiments in Figure \ref{fig:domdep} which all show a narrow region of strong 
precipitation meandering within about 500 km of the SST maximum at the center of the domain,  the large domain experiments 
without the LWCRE have an 8000 km wide region in which the precipitation consistently develops (Figure {\ref{fig:domdep_lwoff}).  
Smaller cells and lines of precipitation develop within this large area with no apparent preference to settle
over the center of the domain where the SST is a maximum.  As previously noted, 
these GCM-like simulations equilibrate after approximately 50 days.  There is also a dramatic change in 
the distribution of precipitation on the $4000\, \rm{km}$ domain simulations after almost 2 years.   The domain mean 
precipitation does not significantly change in these cases, only the spatial structure.

@@

% new Hovmoller diagram
\begin{figure}
 % \includegraphics[angle=90, width=0.95\columnwidth]{walkerfigs/hov_precip_4pan_vert_lwcreon.eps}
  \includegraphics[width=0.95\columnwidth]{walkerfigs/hov_precip_lwon_huge.eps}
  \caption{Evolution of precipitation through 3 years of simulation for experiments with a grid spacing of
  25km and 100km.  Panel A shows the 100km experiment on the large domain (P100L); 
  B, 25km on large domain (P25L); C, 100km on small domain (P100); and D, 25km on small domain 
  (P25).  For each resolution, the only difference between the experiments shown is a domain length of 
  16,000 km or 4,000 km.  All cases have an SST of 301 K at the center and 297K at the edges.  
  The plotted contour values are: 1,5,10,15,20,30,40,50,60,70,80,90.  Data have been averaged over the short horizontal dimension.}
  \label{fig:domdep}
\end{figure}

@@

We now use the mock-Walker circulation to compare GCM-like simulations with CRM-like simulations.  
We focus in this section on simulations with grid-spacing of 1km, 2km, and 25km all on a domain with the width of 4,000 km for the long side.  
The models agree on 
the basic circulation pattern and the spatial distribution of mid-tropospheric condensate.  
However, the E25/P25 simulations produce 4 to 5 times as much low-level cloud and 
condensate as E2/E1 in the subsiding regions.   As a result the models have a different response 
to the LWCRE.  The differences in the boundary layer of the wind, enthalpy flux, and 
temperature among the models result in different spatial distributions and amounts of 
precipitation in the equilibrated state.
